 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Dylan}{Moore}{ \href{mailto:dylantmoore@icloud.com}{dylantmoore@icloud.com} | +1 512 705 0291 | \urlstyle{same}\href{https://github.com/dtm001}{Github} | \urlstyle{same}\href{linkedin.com/in/dtm001}{Linkedin}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyaddress{
3305 Cherrywood Road \\
Austin, TX \\
78722
}

\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear [Hiring Manager],}

% The first paragraph of your job application letter should include information on why you are writing. Mention the job you are applying for and where you found the position. If you have a contact at the company, mention the person's name and your connection here.

\lettercontent{I am writing to express my interest in the Senior Software Engineer position at [Company Name]. With a proven track record of leadership, innovation, and technical expertise, I am confident that my experience will enable me to make significant contributions to your engineering team.
}


   
% The next section of your cover letter should describe what you have to offer the company. Make strong connections between your abilities and the requirements listed in the job posting. Mention specifically how your skills and experience match the job. Expand on the information in your resume.
% Try to support each statement you make with a piece of evidence. Use several shorter paragraphs or bullets rather than one large block of text, which can be difficult to read and absorb quickly.
%For example 

% Using the knowledge and skills I have acquired in my <DEGREE PROGRAM> combined with my technical abilities I believe I can provide significant value to <COMPANY> while providing me invaluable experience to <PREPARE FOR OR FURTHER CAREER>.
% <RELEVANT LIFE STORY/ WORK/ PROJECT >
% In own projects, my coursework, work as a <PREVIOUS JOB TITLE> I have applied knowledge of <SUBJECT MATTER>.
% <LIST OF SMART SOUNDING SKILLS AND TOOLS>.
% Combining these tools with my interests in <FIELD> issues, I hope to help the <DEPARTMENT> answer questions about the <SUBJECT> behind <FIELD> projects.

\lettercontent{As a Software Engineering Team Lead at General Motors, I spearheaded the architecture and development of the Unified Inventory Visibility platform, which significantly reduced operational overhead by replacing third-party contracts worth millions of dollars. My technical leadership has also been instrumental in designing innovative solutions, such as the proposal and implementation of a micro-frontend application architecture. This strategy allowed multiple teams to independently manage their own repositories, development, and deployment cycles. At runtime, a host application dynamically integrates the various micro-frontends, delivering a seamless user experience while providing the flexibility needed for efficient development and adaptation to organizational changes.
}

\lettercontent{I am passionate about working in environments where I am empowered to think outside the box and experiment with new approaches. I take pride in delivering high-quality work that exceeds expectations. I am eager to bring my expertise, collaborative mindset, and problem-solving abilities to your team.}
% Conclude your application letter by thanking the employer for considering you for the position. 

\lettercontent{I would love the opportunity to further discuss how my skills and experiences align with the goals of [Company Name]. Thank you for considering my application. I hope to be able to contribute to your team and help drive continued success.}
\vspace{0.5cm}

\closing{Sincerely, \vspace{-1cm} }

\signature{Dylan Moore}

\end{document}  
\documentclass[]{article}
