%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace} % Import needed for line spacing adjustments
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
    \vspace{2.5mm} % Add vertical space below the overview
}

\newcommand{\jobOverview}[1]{
    \vspace*{-1pt} % Add vertical space above the overview
    \hspace*{1em} % Indent to align with bullet points
    \parbox[t]{\dimexpr\linewidth-3em}{\setstretch{0.9}\item\small{{#1}}} % Format the overview as italic, reduce line height
}

\newcommand{\eduSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4}  \\
      \textit{\small#5} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Dylan Moore} \\ \vspace{10pt}
    \small 3305 Cherrywood Road Austin, TX. 78752
    \vspace{3pt} \\
    \small +1 512 705 0291 $|$ \href{mailto:dylantmoore@icloud.com}{\underline{dylantmoore@icloud.com}} $|$ 
    \href{https://www.linkedin.com/in/dtm001}{\underline{linkedin.com/in/dtm001}} $|$
    \href{https://github.com/dtm001}{\underline{github.com/dtm001}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {General Motors}{Austin, TX}
        {Software Engineering Team Lead}{Jan. 2023 -- Present}
        \jobOverview{Led architecture and development of a unified Inventory Visibility platform, reducing operational overhead by millions through efficient data aggregation, cross-functional collaboration, and streamlined workflows.}
        \resumeItemListStart
           \resumeItem{Spearheaded the migration of on-premise Kubernetes clusters to third-party cloud providers, improving scalability and reliability.}
           \resumeItem{Created an innovative integration test framework for validating OpenSearch query logic, enhancing the accuracy of critical inventory analytics dashboards.}
           \resumeItem{Conducted regular sessions on development practices and design patterns, fostering junior developers' growth and advancing team technical expertise.}
           \resumeItem{Ensured dependency alignment across multiple scrum teams, leading to consistent successful deployments and maintaining green project status.}
        \resumeItemListEnd 

    \resumeSubSubheading
    {Senior Software Engineer}{June 2022 -- Present}
    \jobOverview{Designed and implemented high-performance application features, improving efficiency by 50x and saving significant resources through optimized development and issue resolution processes.}
    \resumeItemListStart
        \resumeItem{Successfully proposed and developed the integration of an OpenSearch indexing layer, boosting application performance by 50x}
       \resumeItem{Led the design and implementation of a micro-frontend framework enabling cross-team development, deployment, ownership, and seamless integration.}
       \resumeItem{Built a VIP inventory ticket tracking system reducing emergency resolution times by 10x and improving critical vehicle delivery.}
    \resumeItemListEnd

    \resumeSubSubheading
    {Software Engineer}{Sept. 2019 -- June 2022}
    \jobOverview{Delivered a company-wide inventory platform, saving millions annually by integrating vehicle life-cycle data into a reliable and scalable "golden source."}
    \resumeItemListStart
        \resumeItem{Delivered a cutting-edge, cloud-native inventory web application, saving millions annually replacing off-the-shelf data visualization solutions for business clients.}
        \resumeItem{Integrated and deployed a golden source of vehicle life-cycle data using a Kafka publish/subscribe model, supporting company-wide data consumption.}
        \resumeItem{Built custom service monitors that ensured high system availability and up-time reliability.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript/JavaScript, Java, Python, Go, C\#, C/C++, SQL} \\
     \textbf{Frameworks}{: React, NextJS, Node.js, NestJS, Spring, Quarkus, .NET} \\
     \textbf{Technologies}{: Docker, Kubernetes, OpenSearch/ElasticSearch, Kafka, Redis } \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \eduSubheading
      {Texas State University}{San Marcos, TX}
      {Bachelor of Arts in Computer Science} {Aug. 2014 -- Aug. 2018} 
      {Minor in Applied Mathematics}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

